Cybercrime and Online Video Games

### 2019-12-13 paper/paper.tex
Update paper.tex

\subsection{Account Sales}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount}
	\caption{Thread Count}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}

>>>>

\subsection{Account Sales}
One of the more common video game hacks is account selling. This isn't giving
a player an unfair advantage but selling hacked accounts to people. It is not 
too uncommon to see somone's account information for sale on hackforums 
without their knowledge. Selling accounts can be a lucrative business and gaining
access to accounts through techniques such as phishing is not the most difficult
form of hacking out there. Given Fortnite's popularity with people under 18, we
feel the game's players are more at risk for these kinds of attacks than for
other online games.

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width = .4\linewidth]{ThreadCount.png}
	\caption{Thread Count}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
 	\centering
	\includegraphics[width=.4\linewidth]{CommentCount.png}
	\caption{Comment Count}
\end{subfigure}
\caption{Thread and Comment Pie Charts}
\end{figure}
